Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
readded my old proposal tex  which has been removed somehow =)

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate proposals cut we can use bottom up hierarchical clustering.
In each step we contract the edge with the highest weight.
Parallel edges are merged into single edges by summing their weights.
We stop when a certain number of nodes is reached, or the
largest edge weight among the not yet contracted edges is smaller then a certain threshold.
To get versatile proposals we either add noise 
to the edge weighs or permute a certain number of weights.

@@

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
%
The edge weighted watershed algorithm \cite{meyer_2013}
with random seeds can be used to get 
cheap proposals. Instead of $n$ seeds distributed uniformly
over all nodes we use the following.
Draw $n/k$ random edges only the negative edges, 
and give the two nodes of each random edge different seeds.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional randomness, noise can be added to
the edge weighs.

>>>>

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate fast energy aware proposals we can use energy
based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
EHC follows the energy function, therefore the \emph{quality}
of the proposals is high.
To get \emph{diversity} among the different proposal,
we add normal distributed noise with a standard deviation of $\sigma_{ehc}$
to each edge weight.
To get proposals of the desired \emph{size}, we can use a
different stop condition in EHC, and stop when a certain number of connected
components is reached.

@@

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
%
The edge weighted watershed algorithm \cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
Draw $n/k$ random edges only the negative edges,
and give the two nodes of each ``seed-edge'' a different seed.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity} randomness, noise can be added to
the edge weighs.
